\abstractzh{
本文聚焦新兴市场情境下资本市场自由化能否因果性推动企业数字化转型。本文以中国A股分阶段纳入MSCI新兴市场指数为制度性冲击，该冲击提升了样本企业面向全球投资者的可得性与关注度，构成具有政策含义的准自然实验。基于2010--2022年2,712家上市公司、35,264个公司-年份观测值，本文采用双向固定效应双重差分（DID）识别策略，并结合事件研究、倾向得分匹配双重差分（PSM-DID）、安慰剂检验与分期处理诊断开展稳健性验证。

本文的核心贡献之一是构建了基于中文年报文本的企业数字化转型测度指标。该指标采用自然语言处理与领域词典方法，覆盖人工智能、大数据、云计算、物联网、区块链/分布式账本与企业数字化推进六类技术集群。为缓解关键词膨胀与战略性披露偏差，本文将文本指标与外部技术相关结果进行效度检验，并结合对数变换、缩尾处理、披露长度标准化指标及替代指标设定进行敏感性分析。

实证结果显示，在优选基准模型下，MSCI纳入使企业数字化转型强度提高0.39个对数点，约相当于处理前水平提升48\%。动态事件研究结果表明，处理前不存在系统性趋势差异，处理后效应持续且具有累积特征。进一步地，安慰剂处理、分期处理诊断、替代聚类标准误、受限样本检验与多口径被解释变量结果均支持核心结论。异质性分析发现，该效应在高技术行业和经济较发达地区更为显著，表明吸收能力与制度互补性会影响自由化收益。机制检验对两条可直接识别的渠道提供一致证据：融资约束缓解，以及外部监督与信息披露纪律强化带来的治理改善。总体而言，本文表明国际金融一体化可作为新兴市场企业数字化升级的重要制度催化机制。
}
{
资本市场自由化；数字化转型；MSCI纳入；中国A股；新兴市场；计算文本分析；双重差分
}

\abstracten{
This thesis investigates whether capital market liberalization can causally promote digital transformation at the firm level within an emerging-market context. The empirical setting involves the phased inclusion of Chinese A-share firms into the MSCI Emerging Markets Index, serving as a policy-relevant institutional shock that increased the exposure of selected firms to global investors. Building upon this quasi-natural experiment, the study integrates an identification-oriented econometric methodology with comprehensive computational measurement to generate evidence that is both causally interpretable and substantively significant. Specifically, the analysis employs a panel comprising 35,264 firm-year observations from 2,712 listed firms spanning the years 2010 to 2022 and estimates treatment effects utilizing a two-way fixed-effects difference-in-differences framework, complemented by event-study dynamics, matching-based diagnostics, and placebo-based falsification.

A central contribution of this thesis is the development of a comprehensive digital transformation outcome metric derived from Chinese annual report text. The metric is constructed employing natural language processing techniques and domain-specific dictionaries encompassing six technology clusters: artificial intelligence, big data analytics, cloud computing, Internet of Things, blockchain/distributed ledger technologies, and enterprise digitization initiatives. To mitigate concerns regarding keyword inflation and disclosure bias, the study validates the text-based indicators against external technology-related outcomes, applies logarithmic transformations and winsorization procedures, and conducts robustness tests using length-normalized outcomes and alternative index formulations.

The baseline results demonstrate that MSCI inclusion enhances digital transformation intensity by 0.39 log points within the preferred specification, which is approximately a 48\% increase relative to pre-treatment levels. Dynamic event-study estimates show no systematic divergence prior to treatment and indicate enduring post-treatment effects, thereby supporting the parallel trends assumption and suggesting a cumulative adjustment process rather than a one-period reporting response. An extensive array of robustness checks, including placebo treatment assignments, staggered adoption diagnostics, propensity-score-matched DID estimation, alternative clustering strategies, restricted-sample tests, and multiple dependent-variable definitions, substantiate this conclusion.

The thesis further explores heterogeneity and mechanistic pathways to transcend average effects. Heterogeneity analyses indicate more pronounced effects in high-technology industries and economically advanced regions, suggesting that absorptive capacity and institutional complementarity influence the benefits of capital market liberalization. Evidence of mechanisms consistently supports two directly testable channels: alleviation of financing constraints and enhancement of governance quality through intensified external oversight and disclosure discipline. Overall, the study demonstrates that international financial integration can serve as an institutional catalyst for corporate digital upgrading in emerging markets.
}
{
Capital market liberalization; Digital transformation; MSCI inclusion; Chinese A-shares; Emerging markets; Computational text analysis; Difference-in-differences
}
