\chapter{Introduction}
\label{chap:introduction}

This chapter introduces the core research problem, motivates its academic and policy relevance, and defines the thesis objectives and scope. It positions the study at the intersection of capital market liberalization and firm-level digital transformation, clarifies why the MSCI A-share inclusion episode provides a suitable quasi-experimental setting, and outlines the empirical and methodological contributions developed in subsequent chapters.

Beyond orientation, the chapter specifies the analytical stance adopted throughout the thesis: digital transformation is treated as an investment process shaped not only by internal managerial capability but also by external capital-market institutions. This framing shifts the research question from \emph{whether} firms transform to \emph{how} financial opening changes the conditions under which transformation becomes feasible, credible, and sustained.

\section{Research Background}

The relationship between capital market liberalization and corporate digital transformation is currently a hot topic, especially in development economics, corporate finance, and technology management. Over the last two decades, governments in emerging nations have gradually opened their domestic financial institutions to international investors. At the same time, firms have been under increasing pressure to digitize production, operations, governance, and customer interactions. Despite the importance of these themes, prior research has often explored them separately rather than together. Financial liberalization research typically focuses on valuation implications, liquidity, and investment efficiency, whereas digital transformation research focuses on internal skills, leadership, and technology readiness~\cite{Fang2024}. The critical question at the intersection of these literatures remains unanswered: can international capital market integration promote firm-level digital transformation, and if so, through which mechanisms?

This thesis is driven by the fundamental question concerning boundaries. It states that digital transformation involves both a financing and governance process, shaped by capital market institutions, as well as a management or technological process. Characteristics of digital transformation programs in many emerging markets include high fixed costs, uncertain returns, prolonged gestation periods, and strong complementarities with management learning~\cite{Chanias2019}. Even when expected social benefits are substantial, these features may introduce funding frictions that potentially hinder or delay adoption~\cite{ChenZhang2024}. Capital markets liberalization might alter the investment considerations of firms contemplating digital upgrades by expanding the investor base, decreasing financing costs, and improving governance~\cite{Barro1990}. Gaining a comprehensive understanding of this connection is essential for both scholarly inquiry and policy making.

The Chinese background is especially important for this research. China features scale, diversity, and institutional growth in ways that make it ideal for empirical study~\cite{Allen2017}. It is one of the world's largest stock markets and a leading hub for industrial digitalization, yet capital account liberalization has mostly been gradual and driven by policy~\cite{PLi2023}. This slow process results in notable policy events with predictable timing. Among these, the inclusion of Chinese A-share firms in the MSCI Emerging Markets Index stands out as a key externally imposed reform that increased firms' exposure to international investors.

The practical reason behind this study is equally strong. Policymakers increasingly view digital transformation as a way to boost productivity and national competitiveness. However, firms vary greatly in their capacity to carry out transformation initiatives~\cite{Liu2023}. Market-opening policies may produce wider technical spillovers than are typically acknowledged if access to global capital and investor networks significantly influences digital adoption~\cite{Zheng2021}. On the other hand, liberalization may increase regional and firm-level disparities in digital capabilities if gains are concentrated among firms that already have advantages. Therefore, a thorough empirical evaluation is required.

Another important motivator is the measurement technique. A large portion of the research on digital transformation is based on managerial evaluations, survey data, or limited proxies like IT spending and patent counts. These metrics frequently have poor comparability over time, self-reporting bias, and restricted coverage~\cite{Wang2022}. In order to create a firm-year digital transformation index from annual report disclosures, this thesis uses a computational text-analysis approach. The project aims to generate evidence that is both strong in identification and wide in coverage by combining this large-scale measuring technique with a quasi-experimental methodology.

According to~\cite{Chen2022}, increased analyst coverage and enhanced information accuracy constitute two mechanisms through which digital transformation augments information environments.~\cite{ChengMasron2023} indicate that regulatory uncertainty can amplify enterprises' digital responses, thereby underscoring the significant influence of external environments on transformation behavior.~\cite{DuWang2024} find that the innovative benefits of digital transformation are substantially strengthened by financial support, particularly via capital markets, with effects that are statistically significant at the 1\% level. While some studies have found reduced equity financing costs for firms that have undergone digital transformation~\cite{ZhangWang2024}, others contend that digital transformation enhances debt financing outcomes and overall firm performance~\cite{XueZhang2024}. Collectively, these findings suggest that the financial outcomes of digital transformation are largely contingent on specific conditions, disclosure quality, and governance frameworks.

While moving beyond correlation-based inference, this study builds on previous research. Most earlier studies focus on a single channel or outcome variable, often without addressing treatment assignment endogeneity. In contrast, this thesis combines mechanism-oriented research, a long panel (2010--2022), and a quasi-experimental policy shock to evaluate whether liberalization can be considered a causal factor in the level of digital transformation. The theory conceptualizes digital transformation as a process of cumulative strategic investment. Over time, firms adjust governance procedures, assess financing constraints, and update expectations. At least three mechanisms are expected for liberalization to influence this process: removing financial restrictions, enhancing governance and transparency standards through international oversight, and expanding access to cross-border knowledge networks. These mechanisms form the foundation of the thesis's empirical framework.

As a result, there are three main motivations. First, it tackles a significant open question in the literature about the relationship between firm-level technological innovation and global finance. Secondly, it offers evidence from a top and emerging economy that is methodologically robust. Third, it provides firms and regulators looking to integrate capital market reform with digital development goals with policy-relevant insight.

\section{Research Questions and Objectives}

In light of the aforementioned motivation, this thesis addresses three relevant research problems.

\begin{itemize}
    \item First, does inclusion in the MSCI Emerging Markets Index, a proxy for capital market liberalization, considerably raise the intensity of digital transformation at the firm level? The main causal question is this one. In comparison to similar untreated organizations, the study assesses whether treated firms see a consistent post-inclusion boost in digital transformation.
    \item Second, do treatment effects vary by technology domain, industry, area, and firm characteristics? Digital transformation is not a single technology, but a collection of investments, each with its own capital intensity and capabilities requirements. The thesis investigates if effects are stronger in domains such as AI, big data, and cloud computing; whether reactions differ across technology-intensive and traditional industries; and whether regional institutional quality influences outcomes.
    \item Third, how does liberalization affect digital transformation? The thesis investigates three channels using theory and prior evidence: funding restrictions, governance and monitoring, and knowledge spillovers. In empirical implementation, this thesis directly tests the first two channels and treats the knowledge channel as a deferred empirical extension requiring direct mediator variables.
\end{itemize}

The methodological objective is to combine proven NLP-based measurement with quasi-experimental econometrics in a transparent, reproducible, and appropriate manner for large-scale panel data. The key objective is to determine whether international financial integration may be used as a stimulus for technological advancement within firms. The policy objective is to offer information to capital market regulators, institutional investors, and corporate executives about the larger technology implications of market-opening changes.

The thesis follows with five operational aims in order to attain these objectives. It generates high-coverage firm-year digital transformation metrics from annual reports. It employs baseline and dynamic DID techniques to assess therapy efficacy. It assesses inference stability by doing robustness and sensitivity tests. It uses heterogeneous effects to identify boundary conditions. It conducts mechanism evaluations to assess financing, governance, and knowledge channels.

\section{The Empirical Setting: China's A-Share Market and MSCI Index Inclusion}

The empirical background for this argument is the gradual inclusion of Chinese A-shares in the MSCI Emerging Markets Index, a watershed moment in China's financial opening process~\cite{YLiu2024}. Prior to 2018, global investors had limited access to China's domestic equity market due to ownership restrictions, quota systems, and market-access frictions. Although conduits such as QFII, RQFII, and the Stock Connect programs existed, broad passive global allocation to mainland A-shares remained limited~\cite{Awokuse2009}.

MSCI inclusion changed this environment by connecting eligible A-share companies to benchmark-driven international capital flows~\cite{Wei2020}. MSCI indexes are often used by global institutional investors and index-tracking funds. Being included in the MSCI Emerging Markets Index affects active portfolio building, analyst focus, and investor relations practices, in addition to passive investment flows~\cite{PLi2023}. The reform therefore modified firms' exposure to external financing and oversight conditions in a way that is economically significant.

Phases of the inclusion procedure developed, which is useful for identification. Phase~I was put into effect in June 2018 with 234 large-cap A-shares at a 5\% inclusion factor after the June 2017 announcement. By November 2019, Phase~II increased coverage to 472 securities with a higher inclusion factor. Clear treatment time and observable pre- and post-policy windows have been established by this phased implementation. One major advantage of this system is that inclusion criteria were mostly rule-based and established externally. Eligibility was based on market capitalization, liquidity, and Stock Connect accessibility rather than on discretionary judgments of corporations' digital strategies~\cite{Yang2025}. While no real-world situation is completely random, this institutional setup increases the likelihood that inclusion reflects exogenous variation in international capital access relative to firms' digital transformation paths.

China is also an ideal context because firms operate under substantial heterogeneity in regional development, industry composition, ownership structures, and governance quality. This heterogeneity allows the thesis to test whether liberalization effects are uniform or conditional on absorptive capacity~\cite{Dong2023}. Prior studies indicate that effects are often stronger in specific contexts, such as non-Eastern regions in some financing-related analyses, and among non-state or non-SME firms in others. Embedding these moderation patterns within the MSCI setting helps move beyond average treatment effects toward a richer understanding of distributional outcomes.

\section{Overview of Research Design and Data}

The empirical design combines causal identification with large-scale computational measurement. The main approach is a two-way fixed effects difference-in-differences model comparing firms that are included in MSCI (treated) and those that are not (untreated) before and after inclusion. This baseline is supplemented by event-study estimation to evaluate dynamic responses and pre-trend validity, propensity score matching DID to enhance comparability on observables, and placebo-based inference checks.

The data cover 35,264 firm-year observations from 2010 to 2022, representing 2,712 Chinese listed firms after sample cleaning. Core financial and governance variables are drawn from CSMAR, while treatment status is derived from MSCI constituent lists. Digital transformation outcomes are constructed from annual-report text using NLP-based keyword extraction across six technology domains: AI/machine learning, big data, cloud computing, IoT, blockchain/distributed ledger technologies, and enterprise digitization programs.

The baseline outcome is a composite index using log transformation of aggregated keyword frequencies. This approach addresses right skewness and enhances interpretability when disclosure dispersion is high. For robustness, alternative outcomes are also used, including domain-specific indices, normalized measures adjusted for report length, and additional transformations to assess sensitivity to scaling choices.

Mechanism analysis is embedded in the design rather than added as a descriptive task. Proxies related to financing constraints and governance quality are estimated through structured regressions to check whether channel patterns match the conceptual framework. The knowledge-spillover channel is retained at the theoretical level but not directly estimated in the baseline because direct mediator variables are not yet available in the merged panel.

Overall, the research design is deliberately triangulated: one treatment setting, multiple estimators, multiple outcome measures, and various mechanism tests. This triangulation enhances confidence that the results reflect genuine economic effects rather than model-specific artifacts.

\section{Significance of Research}

This study is significant for three strands of literature: capital market liberalization, digital transformation economics, and computational empirical methods.

\begin{itemize}
    \item First, it expands the liberalization literature beyond traditional market results. Previous research often focuses on liquidity, valuation, return co-movement, or financing costs. This study demonstrates that liberalization can affect firms' technological paths, thus connecting financial integration to long-term productivity-related behavior.
    \item Second, it advances the digital transformation literature by highlighting external financial environments as a key factor in shaping corporate digital strategy. While much existing research focuses on internal capabilities, managerial cognition, and organizational change, this thesis demonstrates that access to international capital and investor oversight can significantly influence the speed and direction of transformation.
    \item Third, it offers mechanism-level evidence that directly tests financing and governance channels under a common treatment design, while preserving knowledge spillovers as a theoretically grounded channel for future direct testing.
    \item Fourth, the thesis enhances methodology by combining quasi-experimental causal inference with validated Chinese-language text analytics at scale.
    \item Fifth, it contributes to the emerging-market comparative literature by offering high-resolution evidence from China.
    \item Sixth, it provides policy implications based on micro-level evidence. Regulators interested in the broader development impact of capital market reform can use these findings to assess whether market-opening policies promote strategic upgrading.
\end{itemize}

\section{Thesis Structure}

The thesis is organized in seven chapters, with each chapter designed to build logically on the previous one.

\begin{itemize}
    \item \textbf{Chapter~1} introduces the research problem, motivation, questions, objectives, empirical setting, and expected contributions.
    \item \textbf{Chapter~2} develops the literature review. It synthesizes foundational and recent studies on liberalization, digital transformation, mechanism channels, and text-based measurement.
    \item \textbf{Chapter~3} presents institutional background and formal hypothesis development. It details China's pre-liberalization capital market structure, the MSCI inclusion process, and the quasi-experimental properties of the reform.
    \item \textbf{Chapter~4} introduces Research Design~I focused on causal identification. It describes sample construction, variable definitions, treatment assignment, baseline and dynamic model specifications, and descriptive statistics.
    \item \textbf{Chapter~5} introduces Research Design~II focused on computational measurement. It documents corpus construction, Chinese text segmentation, dictionary design, index construction, and validity diagnostics.
    \item \textbf{Chapter~6} reports empirical results and discussion. It presents baseline effects, event-study dynamics, robustness checks, heterogeneity analyses, and mechanism evidence.
    \item \textbf{Chapter~7} concludes with a synthesis of findings, original contributions, limitations, and future research directions.
\end{itemize}
