\chapter{Literature Review}
\label{chap:literature_review}

This chapter develops the theoretical and empirical foundation of the thesis by integrating research on capital market liberalization, digital transformation, and computational measurement. It reviews the main channels through which international capital access can influence firm behavior, evaluates contextual differences in existing evidence, and identifies unresolved gaps in causal identification and mechanism integration.

\section{Capital Market Liberalization: Theory and Evidence}

\subsection{Theoretical Foundations of Financial Liberalization}

Capital market liberalization generally refers to removing barriers that separate domestic financial systems from international portfolio flows~\cite{Long2024}. In theory, opening equity markets can improve allocative efficiency by channeling capital toward more productive firms, reducing financing costs through broader investor participation, and improving risk sharing through more diversified ownership structures~\cite{Zhu2023}. The standard welfare argument predicts stronger gains for firms facing tighter financing constraints~\cite{Yin2023}. In segmented markets, limited domestic savings, home bias, and information frictions can keep external finance expensive. Liberalization can reduce these distortions by intensifying investor competition and deepening market liquidity~\cite{HLiu2024}.

Theoretical work also highlights important non-linearities. The benefits of liberalization depend on institutional quality, legal enforcement, disclosure standards, and market infrastructure~\cite{Stiglitz2004}. Where institutions are weak, liberalization may amplify volatility or redirect resources toward short-horizon opportunities rather than long-horizon productive investment~\cite{JXZhang2023}. At the firm level, liberalization changes the optimization environment facing managers and controlling shareholders~\cite{ChengMasron2023}: it affects the cost of external finance, investor horizons, and the intensity of external monitoring~\cite{Chen2025}.

The MSCI inclusion mechanism is particularly informative because it combines signaling and flow effects. Inclusion can automatically trigger passive fund allocations while simultaneously signaling market quality and investability to active global investors.

\subsection{Effects on Corporate Investment, Innovation, and Governance}

Empirical studies generally find that market opening influences corporate behavior through investment and governance channels~\cite{Tian2023}. On the investment side, reduced financing frictions can broaden firms' feasible project options~\cite{RZhang2023}. Firms may increase R\&D, capital expenditure, and strategic intangible investments when expected financing constraints lessen~\cite{Yin2023}. On the governance side, foreign institutional investors can strengthen monitoring and raise transparency expectations.

Evidence from prior work supports this logic. Chen et al.~\cite{Chen2022} show that digital transformation is associated with higher analyst coverage and improved information accuracy. Du and Wang~\cite{DuWang2024} provide direct evidence that financial support strengthens the innovation effects of digital transformation, particularly in environments with tighter conventional financing constraints. Chen and Zhang~\cite{ChenZhang2024} and Feng et al.~\cite{Feng2024} extend this argument to firms' financing structures.

\subsection{Evidence from Emerging Market Contexts}

Emerging markets provide valuable evidence because they combine high growth potential with institutional frictions that highlight financing channels. Studies in these markets often detect stronger real effects of financial reforms compared to more developed markets where constraints are already less severe~\cite{StiglitzOcampo2008}. The Chinese evidence is especially useful due to detailed data and specific policy information~\cite{Yan2023}. However, a direct causal link from liberalization shocks to firm-level digital transformation outcomes is less developed.

Zhang et al.~\cite{Zhang2024} show that contextual heterogeneity is central: estimated effects vary with regional market development, ownership structure, and firm size. This pattern implies that pooled average treatment estimates may mask economically meaningful distributional differences. Stiglitz~\cite{Stiglitz2000} similarly emphasizes that policy shocks interact with organizational absorptive capacity.

\section{Digital Transformation: Conceptual Framework and Determinants}

\subsection{Defining Digital Transformation: Technological and Organizational Dimensions}

Digital transformation is more than technology acquisition. It is an ongoing, firm-wide reconfiguration of value creation, operations, and organizational coordination through digital technologies~\cite{Yang2023}. A narrow input-based view focused only on hardware and software spending misses the strategic and organizational conditions that determine whether digital investment translates into productivity gains. Conceptually, the process has at least three layers~\cite{Verhoef2021,XueZhang2024}: infrastructure adoption, process transformation, and organizational transformation.

These layers depend on each other. Infrastructure without process integration can yield limited results~\cite{WangLi2024}. Process changes without organizational incentives can prevent progress. Organizational commitment without funding can remain superficial~\cite{XueZhang2024}. Therefore, digital transformation is best viewed as a coordinated investment journey rather than a single technological event~\cite{Chanias2019}.

\subsection{Core Technology Domains: AI, Big Data, Cloud Computing, IoT, and Blockchain}

The technology areas highlighted in this thesis align with key trends in modern corporate digital transformation. Artificial intelligence and machine learning support prediction, optimization, and automation across both front-end and back-end operations~\cite{Babina2024}. Big data systems enable companies to turn large, fast-moving information into operational insights. Cloud computing offers scalable infrastructure that reduces fixed ICT costs~\cite{Adeola2020}. Internet of Things technologies link physical assets to digital monitoring and control systems~\cite{Kommisetty2022}. Blockchain and distributed ledger technology provide traceability, tamper resistance, and coordination across organizational boundaries~\cite{Ansari2025}. Enterprise digitization initiatives combine these technologies with ERP upgrades, process engineering, and platform strategies.

Empirically, these domains are related but not interchangeable margins of transformation. AI/ML and advanced analytics are usually data- and talent-intensive, with higher setup costs and longer learning curves. Cloud adoption often lowers entry barriers and accelerates deployment, while IoT initiatives require coordinated redesign of software and physical production systems. Blockchain applications are often narrower, but can be highly relevant in traceability-intensive supply chains. As a result, measured digital intensity can move at different speeds across domains even under similar financing conditions~\cite{Wang2024,Ren2024}.

This heterogeneity implies that aggregate digital indices should be interpreted as averages over technologies with different risk profiles, adjustment speeds, and implementation bottlenecks, rather than as a single homogeneous investment decision. That interpretation is important for later empirical sections, where treatment effects are estimated on both composite and technology-specific outcomes.

\subsection{Drivers, Barriers, and Firm-Level Heterogeneity}

Drivers of digital transformation include financial slack, managerial capability, data infrastructure, and complementary human capital. Recent studies also emphasize organizational execution quality: cross-functional coordination, digital leadership commitment, and internal data-governance standards all increase the probability that projects scale beyond pilot stages~\cite{ZhangCao2023}.

Barriers are equally important. High uncertainty about payoffs can delay investment, especially for firms under pressure to meet short-horizon performance targets. Talent shortages in data engineering, AI deployment, and cybersecurity create bottlenecks that raise implementation risk~\cite{ZhangCao2023}. Legacy IT architectures and fragmented databases further increase integration costs and extend rollout cycles.

These frictions imply heterogeneous response capacities. Larger firms may capture stronger scale economies in platform investment and digital talent recruitment~\cite{Gao2024}. Firms in economically developed regions may access deeper supplier ecosystems and larger pools of specialized labor. By contrast, resource-constrained firms may prioritize modular adoption and postpone system-wide upgrades.

Ownership and market structure also matter. Non-state firms often face tighter product-market discipline, which can strengthen incentives to adopt productivity-enhancing digital strategies~\cite{Jin2023}. Overall, the literature indicates that average effects can conceal substantial cross-sectional dispersion, motivating explicit heterogeneity analysis by region, industry, and firm characteristics in the empirical chapter.

\subsection{Digital Transformation in Emerging Markets: Opportunities and Constraints}

Emerging markets offer a digital transformation landscape with both growth opportunities and structural constraints~\cite{Zhao2023}. In these settings, access to external capital markets can play a catalytic role. International investors may provide not only financing, but also governance pressure, benchmarking standards, and stronger emphasis on long-horizon capability building~\cite{Li2025}.

At the same time, external financing does not mechanically translate into successful digital upgrading. The pass-through from capital access to implementation depends on absorptive capacity, including managerial quality, organizational readiness, and local complementary infrastructure. This mechanism helps explain why treatment effects differ materially across firms and regions in emerging economies.

China is especially informative because advanced digital ecosystems coexist with substantial regional and firm-level inequality in capabilities and financing conditions~\cite{Du2024}. This combination provides a strong context for identifying not only whether liberalization affects digital transformation, but also where and for whom the effect is strongest.

\section{Mechanisms Linking Capital Market Liberalization to Digital Transformation}

\subsection{The Financing Constraint Channel}

The financing-constraint channel is the most direct link between liberalization and digital transformation. Digital programs often require substantial upfront spending on software systems, data architecture, cloud migration, machine-learning platforms, and organizational training~\cite{Kose2003}. By broadening access to equity investors and lowering required returns, liberalization can reduce the user cost of capital for these investments~\cite{LiPang2023}.

Existing studies provide direct support for this channel. Hordofa~\cite{Hordofa2024} shows that capital-market financial support significantly strengthens the innovation effects of digital transformation, while Liu~\cite{YLiu2024} documents lower equity financing costs among firms undergoing digital upgrading. Together, these findings suggest that financing and digital transformation are mutually reinforcing. The channel is unlikely to be homogeneous across firms: firms with initially binding financing constraints should exhibit larger responses~\cite{Huang2023}.

\subsection{Corporate Governance and International Investor Monitoring}

A second mechanism is governance upgrading through international investor monitoring. Foreign institutional investors often demand higher disclosure quality, stronger board accountability, and clearer strategic communication~\cite{Chen2025}. Under these conditions, managers face stronger incentives to prioritize long-term value-enhancing projects and reduce agency-driven underinvestment.

Ma et al.~\cite{Ma2025} provide supporting evidence that digital transformation is associated with improved information environments through increased analyst coverage. Li~\cite{CLi2023} further shows that governance effects can interact with ownership structure.

\subsection{Knowledge Spillovers and Global Best Practice Diffusion}

A third mechanism operates through information and knowledge spillovers. Capital market liberalization boosts interactions between domestic firms and global investors, analysts, and intermediaries~\cite{Zheng2021,Zhu2023}. Through investor meetings, analyst reports, benchmarking exercises, and governance engagement, firms can access implementation templates and performance standards~\cite{Sun2022}. This mechanism aligns with broader themes in the literature~\cite{HLiu2024,LiShen2021,WangWang2026}. Evidence from competitive manufacturing environments further suggests that digital-technology spillovers can be strategically state-dependent across rival firms rather than mechanically uniform~\cite{LiuGu2026}.

\subsection{Market Signaling, Certification, and Reputational Effects}

Liberalization can affect digital transformation through signaling and certification processes. Inclusion in a major global benchmark is often interpreted as recognition of minimum standards in accessibility, liquidity, and market relevance~\cite{CLi2023}. This signal can lower external uncertainty about firm quality. Dong~\cite{Dong2023} further distinguishes substantive transformation from symbolic signaling, an important distinction when interpreting post-inclusion disclosure behavior.

\section{Text-Based Measurement of Firm Characteristics}

\subsection{Computational Approaches in Corporate Finance and Economics}

The rise of text-as-data methods has revolutionized empirical corporate research by enabling high-frequency, large-sample analysis~\cite{Yang2024}. In the era of digital transformation, computational text methods are especially valuable because direct accounting measures are often incomplete~\cite{Bellstam2017}. Methodologically, text-based approaches enhance scalability and consistency compared to purely manual coding~\cite{Ahci2023}. However, computational methods need careful validation~\cite{Zimmermann2023}.

\subsection{NLP-Based Measurement of Innovation and Digital Activity}

Afzal~\cite{Afzal2024} shows that Chinese-language annual reports can provide credible NLP-based indicators of digital activity. Kumar~\cite{Kumar2024} further argues for domain-cluster keyword extraction rather than generic buzzword counts. Li et al.~\cite{YLi2023} position NLP-based measurement as a complement to, rather than a substitute for, financial indicators.

\subsection{Validation Strategies for Text-Derived Indices}

Validation is central to any text-based empirical strategy. This thesis applies three validation layers: content validity, construct validity, and robustness validity. Content validity is established through careful dictionary design and expert review. Construct validity is evaluated by comparing text-derived indices with related observable variables. Robustness validity is assessed through alternative outcome definitions and algorithmic specifications.

\subsection{Challenges in Chinese-Language Disclosure Environments}

Chinese-language textual analysis presents technical and interpretive challenges~\cite{YLi2023,Wang2022}. Chinese text segmentation is complex because characters are written without spaces. Another challenge is variation in strategic disclosure~\cite{Yang2024}. A third challenge involves distinguishing between intention and implementation.

Despite these challenges, Chinese annual reports remain some of the most comprehensive and standardized data sources for long-term firm-level analysis. With careful design and validation, they offer a strong empirical foundation for studying digital transformation at scale.

\section{Research Gaps and Positioning of This Study}

The literature review points to four core gaps that motivate this thesis.

\begin{itemize}
    \item \textbf{Linkage gap}: Research on capital market liberalization and research on digital transformation have mostly developed independently.
    \item \textbf{Identification gap}: Many studies rely on cross-sectional correlations or panel models that may face endogeneity issues.
    \item \textbf{Mechanism integration gap}: Existing evidence suggests financing, governance, and knowledge channels are all plausible but often examined in isolation.
    \item \textbf{Measurement scalability gap}: Direct digital investment metrics are often incomplete in emerging-market accounting systems.
\end{itemize}

This thesis addresses these gaps by treating MSCI A-share inclusion as a near-natural experiment to identify the causal effect of liberalization on digital transformation. The reviewed evidence supports this positioning, but prior work rarely integrates these insights within a single coherent design. This thesis is structured to provide that integrated causal framework.
