\chapter{Institutional Background and Hypothesis Development}
\label{chap:institutional_background}

This chapter establishes the institutional context and formal hypothesis structure underpinning the empirical analysis. It first explains the pre-liberalization structure of China's A-share market and the role of Stock Connect as implementation infrastructure for foreign participation. It then details the MSCI inclusion timeline and rule-based eligibility criteria, highlighting why the reform provides plausibly exogenous variation in international capital access. Finally, the chapter translates the conceptual framework from Chapter~\ref{chap:literature_review} into explicit testable hypotheses.

\section{China's Capital Market Structure Prior to Liberalization}

\subsection{The A-Share Market and Domestic Investor Segmentation}

China's A-share market---the renminbi-denominated equity market listed on the Shanghai and Shenzhen Stock Exchanges---was historically subject to strict foreign ownership restrictions and capital controls, which created near-complete segmentation from international capital flows~\cite{Cheng2024}. Before liberalization reforms, foreign investors could access mainland Chinese equities only through the limited QFII (Qualified Foreign Institutional Investor) and RQFII programs, which imposed strict quotas and administrative barriers. This segmentation meant that Chinese listed firms relied almost entirely on domestic capital markets, characterized by shorter investment horizons, weaker corporate governance standards, and limited exposure to global best practices.

\subsection{Stock Connect Programs as the Technical Infrastructure for Liberalization}

The technical infrastructure for capital market liberalization was established through the Stock Connect programs: Shanghai--Hong Kong Stock Connect (launched November 2014) and Shenzhen--Hong Kong Stock Connect (launched December 2016)~\cite{WangChia2014}. These programs developed daily and aggregate quotas, currency hedging methods, and settlement protocols that approved foreign investors to buy A-shares while adhering to capital control regimes. By 2018, these systems were sufficiently developed to handle the substantial capital movements associated with MSCI inclusion~\cite{Yin2023}.

\section{The MSCI Emerging Markets Index and the A-Share Inclusion Process}

\subsection{MSCI as a Global Benchmark: Scale, Influence, and Index Composition}

The MSCI Emerging Markets Index is the main benchmark for global institutional investors investing in developing market equities, with about \$1.9 trillion in assets under management tracking or comparing against MSCI emerging market indices in 2018. The index's composition determines mandatory portfolio allocations for passive funds and acts as a reference for active managers, influencing capital flows to the included companies~\cite{Wei2020}.

\subsection{Inclusion Criteria: Market Capitalization, Liquidity, and Stock Connect Accessibility}

MSCI's inclusion criteria were mechanical rather than discretionary: (i) a minimum free-float adjusted market capitalization threshold; (ii) minimum liquidity requirements based on annualized trading volume and turnover ratios; and (iii) accessibility through Stock Connect programs. Importantly, these criteria are independent of firms' underlying digitalization paths or performance, offering a plausible source of exogenous variation in international capital access.

\subsection{Pre-Announcement and Phased Implementation Timeline}

MSCI announced the inclusion decision on June 20, 2017---a full year before the first implementation tranche---providing firms with time to prepare for international investor engagement. The announcement itself constitutes a clean event that allows testing of announcement effects separately from implementation effects~\cite{Hu2018}.

\subsection{Phase~I (June 2018): 234 Large-Cap A-Shares at 5\% Inclusion Factor}

The initial tranche, launched on June 1, 2018, incorporated 234 large-cap A-shares at a 5\% inclusion factor. This accounted for about 0.73\% of the total MSCI Emerging Markets Index. The modest size aimed to evaluate market preparedness and reduce impact, while allowing the included companies to experience international passive fund inflows for the first time.

\subsection{Phase~II (November 2019): Expansion to 472 Securities at 20\% Factor}

By November 2019, the index grew to include 472 A-shares across large, mid, and small-cap categories, with a 20\% inclusion rate. This significantly boosted the presence of Chinese stocks in the index and broadened the scope to include smaller firms, expanding the universe of treated firms.

\subsection{Quasi-Experimental Properties of the Inclusion Design}

Three features make MSCI inclusion an almost perfect quasi-experiment. First, the selection criteria are mechanical and unrelated to digitalization propensity. Second, the timeline was externally imposed by MSCI, independent of Chinese government or firm decisions. Third, the phased implementation establishes clear pre- and post-treatment periods and multiple cohorts, enabling staggered adoption analysis.

\section{Hypothesis Development}

Building on the theoretical considerations and institutional background outlined above, we develop three testable hypotheses.

\subsection{H1: Main Effect --- Capital Market Liberalization and Digital Transformation Intensity}

\textbf{Hypothesis 1 (H1 --- Main Effect):} Capital market liberalization, proxied by MSCI inclusion, increases firm-level digital transformation intensity.

The causal mechanism is that MSCI inclusion changes firms' investment optimization environment. Inclusion broadens access to external equity capital, improves liquidity, and reduces expected financing costs for long-horizon intangible projects. Because digital transformation programs involve high fixed costs, delayed payoffs, and implementation uncertainty, a reduction in financing frictions should expand the set of digital projects with positive expected net present value. At the same time, exposure to international investors raises disclosure and governance standards, increasing managerial accountability for strategic investment quality. If this mechanism is valid, treated firms should exhibit a post-inclusion increase in digital transformation intensity relative to otherwise comparable non-treated firms.

\emph{Empirical implication:} In the baseline DID and event-study designs, the coefficient on the treatment interaction should be positive, and post-treatment dynamic effects should remain above pre-treatment coefficients if the mechanism reflects sustained investment adjustment rather than short-run disclosure noise.

\subsection{H2: Technology Heterogeneity --- Capital- and Knowledge-Intensive Domains}

\textbf{Hypothesis 2 (H2 --- Technology Heterogeneity):} The liberalization effect is stronger in capital-intensive and knowledge-intensive digital domains than in less demanding domains.

The mechanism linking liberalization to domain-specific outcomes is implementation intensity. Technologies such as cloud infrastructure, AI systems, and large-scale data architecture require substantial up-front capital, specialized human resources, and iterative organizational learning. These characteristics create stronger dependence on financing quality and access to advanced managerial knowledge. In contrast, lower-complexity digital applications generally require smaller irreversible commitments and can be implemented with weaker external support. Therefore, if capital market liberalization operates through financing and knowledge channels, treatment effects should be disproportionately concentrated in high-capital and high-knowledge technology clusters.

\emph{Empirical implication:} In technology-specific regressions, coefficients should be larger in capital- and knowledge-intensive domains (e.g., AI, cloud, and big-data-related indicators) than in lower-complexity domains.

\subsection{H3: Regional and Firm Heterogeneity --- Absorptive Capacity and Institutional Quality}

\textbf{Hypothesis 3 (H3 --- Regional and Firm Heterogeneity):} The effect of capital market liberalization on digital transformation is moderated by regional institutional quality and firm-level absorptive capacity.

The causal pathway requires not only capital access but also conversion capability. Regions with stronger market institutions, deeper digital infrastructure, and richer talent pools allow firms to translate external capital and monitoring into real operational upgrading more efficiently. At the firm level, larger scale, stronger governance, and prior organizational capabilities reduce adjustment costs and improve implementation discipline, making it easier to convert financing opportunities into sustained digital investment. In weaker institutional or capability settings, part of the treatment shock is absorbed by implementation frictions, resulting in smaller observed effects. Accordingly, the same liberalization shock is expected to generate heterogeneous responses across regions, industries, and firm types.

\emph{Empirical implication:} Interaction and subgroup analyses should show stronger treatment effects for firms in institutionally developed regions, technology-intensive industries, and firms with higher absorptive capacity proxies.
