\appendix

\chapter*{Appendix}
\label{chap:appendix}
\phantomsection
\addcontentsline{toc}{chapter}{Appendix}
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\arabic{section}.\arabic{subsection}.\arabic{subsubsection}}

\section{Projects Participated in During the School Period}

\begin{enumerate}
    \item 2023-09-14 (Online, Tencent Meeting): Getting Started as a Research Novice, Speaker: Zhang Jun (Anhui University of Technology).
    \item 2023-12-06 (2n311): Golden Opportunity in the Digital Age! Career and Development Prospects in Database Technology, Speaker: Jia Xinhua (Alibaba Cloud).
    \item 2023-12-06 (2n311): AI Makes Databases Run ``Faster and Further'', Speaker: Dai Jian (Alibaba Cloud).
    \item 2024-10-23 (Venue not specified): Yongchao Forum: Topic Selection and Writing for Economics and Management Academic Papers, Speaker: Yu Liping (Zhejiang Gongshang University).
    \item 2024-11-08 (25-418): Yongchao Forum: Frontier Issues in Science and Technology Development and Reflections on China's Science Evaluation Reform, Speakers: Li Xiaoxuan and Xu Fang (CAS Institutes of Science and Development).
    \item 2024-11-14 (2-S343): Yongchao Forum: Frontier Research Perspectives on Digital-Intelligent Transformation in Manufacturing, Speaker: Li Xueling (Jilin University).
    \item 2025-10-23 (25-1816): Perspective Taking to Promote Work Design: Research Journey and Inspirations, Speaker: Meng Liang (Shanghai International Studies University).
\end{enumerate}

\section{Exploratory Knowledge Spillover Proxy Test}

To align the empirical design with recent spillover studies~\cite{WangWang2026,LiuGu2026} while preserving identification discipline, this appendix reports an exploratory proxy test using currently available merged variables. The proxy is leave-one-out peer digital transformation within industry-year cells:
\begin{equation}
\label{eq:peer_dt_appendix}
\mathrm{PeerDT}_{i,t}^{\mathrm{(ind,loo)}} = \frac{\sum_{j \in (\mathrm{ind},t),\, j \neq i} DT_{j,t}}{N_{\mathrm{ind},t} - 1}
\end{equation}
and the exploratory interaction is $\mathrm{MSCI}_{i,t} \times \mathrm{PeerDT}_{i,t}^{\mathrm{(ind,loo)}}$.

\begin{table}[htbp]
\centering
\caption{Appendix: Exploratory Knowledge Spillover Proxy Regression}
\label{tab:appendix_spillover_proxy}
\small
\begin{tabular}{lccc}
\toprule
\textbf{Variable} & \textbf{Coeff.} & \textbf{(SE)} & \textbf{$p$-val} \\
\midrule
MSCI (treatment exposure) & $-$2.0000 & 1.8336 & 0.2754 \\
PeerDT (industry-year leave-one-out mean) & 0.7046*** & 0.0689 & 0.0000 \\
MSCI $\times$ PeerDT & 0.2342 & 0.1481 & 0.1138 \\
\midrule
Observations & \multicolumn{3}{c}{31,110} \\
Unique firms (cluster level) & \multicolumn{3}{c}{3,921} \\
$R^2$ & \multicolumn{3}{c}{0.3556} \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\item \textit{Notes:} OLS with firm-clustered standard errors; controls include size, ROA, cashflow/assets, Tobin's $Q$, independent directors, and ownership HHI, with industry, province, and year fixed effects. The interaction coefficient is positive but statistically insignificant, so this table is interpreted as exploratory context rather than direct mechanism identification.
\end{tablenotes}
\end{table}
